### 2019-02-01 thesis_report/results.tex
fixed thesis fig for ci

% -*- root: ./report.tex -*-
\chapter{Results \& Discussion}
		In this chapter, we show how the properties of the system change under introduction of the zigzag geometry.
		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter.

>>>>

% -*- root: ./report.tex -*-
\chapter{Results \& Discussion}
		In this chapter, we show how some properties of the system change by introduction of the zigzag geometry.
		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter\ref{}.
